# Exercise 4
## Data Analysis

#### Access the MASS package

```{r results='hide', message=FALSE, warning=FALSE}
library(MASS)
#install.packages('corrplot')
library(corrplot)
```

#### Then read the Boston data from the Mass Package, its in R studio memory, so i can directly fetch them.
```{r}
# load the data
data("Boston")

# explore the dataset
str(Boston)
dim(Boston)
```

We see that we have numerical and interger variables. So we have 506 rows and 14 columns.

#### Now we see the summary of the Boston data and also plot correlation between each variables. 

```{r}
summary(Boston)

# calculate the correlation matrix and round it
cor_matrix<-cor(Boston) 

# print the correlation matrix
cor_matrix<- round(cor_matrix, 2)

# visualize the correlation matrix
corrplot(cor_matrix, method="circle")
corrplot(cor_matrix, method="circle", type='upper')
corrplot(cor_matrix, method="circle", cl.pos = "b", tl.pos = "d",tl.cex = 0.6)
```
The figure above shows that   
there is high correlation between "rad" index of accessibility to radial highways and   
"tax" full-value property-tax rate per \$10,000.  
There is high negative correlation between "lstat" lower status of the population (percent) and  
"medv" median value of owner-occupied homes in \$1000s  

This data frame contains the following columns:  
crim =per capita crime rate by town.  
zn = proportion of residential land zoned for lots over 25,000 sq.ft.  
indus = proportion of non-retail business acres per town.  
chas = Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).  
nox = nitrogen oxides concentration (parts per 10 million).  
rm = average number of rooms per dwelling.  
age = proportion of owner-occupied units built prior to 1940.  
dis = weighted mean of distances to five Boston employment centres.  
rad = index of accessibility to radial highways.  
tax = full-value property-tax rate per \$10,000.  
ptratio = pupil-teacher ratio by town.  
black = 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.  
lstat = lower status of the population (percent).  
medv = median value of owner-occupied homes in \$1000s  

 