# Data wrangling and analysis

Install package and run library
install.packages(ggplot2)
```{r}
library(ggplot2)
```

#Data Wrangling 1 

Now reading data from web
```{r}
students2014  <- read.table("http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/learning2014.txt", sep=",", header =T)
```
Structure of the data
```{r}
str(students2014)
```
So it has "gender" column as Factor and "age" and "points" columns as integer, rest of the columns are numeric.

Dimension of the data
```{r}
dim(students2014)
```
It has 166 rows and 7 columns

Names of columns
```{r}
names(students2014)
```

#Data Wrangling 2 

```{r}
   dim(students2014)
```
Plot the variables
Lets visualize the attitude versus points and colors are given based in gender 

```{r}
library(ggplot2)
#initialize plot with data and aesthetic mapping
p1 <- ggplot(students2014, aes(x = attitude, y = points, col=gender))
#define the visualization type (points)
p2 <- p1 + geom_point()
#draw the plot
p2
```
Figure shows that the attitude and points are linearly related

See the summary of the data
```{r}
summary(students2014) 
```
There are 110 female and 56 male

#Data Wrangling 3

Create a model
```{r}
Model1<- lm(points ~ gender+age+attitude, data = students2014)
```

Create a summary
```{r}
summary(Model1)
```

Only "attitude"" is significant, so we will remove "gender" and "age" from the model
Now i try to include rest of the variables except "gender" and "age" and see its significance.

```{r}
Model2<- lm(points ~ attitude+deep+stra+surf, data = students2014)
summary(Model2)
```
Now we see that except "attitude" all other variables are insignificant
So we make a model 3 by just using "attitude" as predictor variables

```{r}
Model3<- lm(points ~ attitude, data = students2014)
summary(Model3)
```



